---
title: "Figures"
author: "Kelsey Jensen"
date: "2/21/2022"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)

load("../data/priming_calcs.RData")
load("../data/cumu_resp.RData")
load("../data/cumu_resp_long.RData")
load("../data/lineplot_data.RData")
load("../data/barplot_data.RData")
load("../data/baseC_data.RData")
load("../data/mean_baseC_data.RData")
load("../data/mean_mineralization.RData")


```


```{r, echo = FALSE,warning = FALSE, message = FALSE}
plot_theme <- theme(legend.text = element_text(size=12),
                    legend.title = element_text(size=14),
                    axis.line = element_line(colour = "black"),
                    axis.text.y = element_text(size=12, face="bold"),
                    axis.title.y=element_text(size=14, face="bold"),
                    axis.text.x = element_text(size=14, hjust = .5, vjust=0), 
                    axis.title.x=element_text(size=14, face="bold"),
                    axis.ticks = element_blank()
                    )

plant.labs <- c("Interspace", "L. tridentata")
names(plant.labs) <- c("INSP", "LATR")

amend.labs <- c("Control", "Glutamic Acid")
names(amend.labs) <- c("ctrl", "glu")

tmt.labs <- c("Ambient", "Elevated")
names(tmt.labs) <- c("ambient", "elevated")


```

Basic characteristics of each soil type

```{r, echo= FALSE, warning = FALSE, message=FALSE}
plot_soc <- priming_calcs %>% filter(time_fct == "4") %>% 
  ggplot(aes(x = treatment, y= soc_mgC )) + geom_boxplot() +
  facet_grid(~plant, labeller = labeller(plant = plant.labs))+
  xlab(element_blank())+
  stat_compare_means(method = "t.test") +
  theme_bw()+ plot_theme + 
  theme(strip.text.x = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/soc_mgC.png",
      plot= plot_soc, dpi = 300, width = 8, height = 5, units = "in")

plot_socisoC <- priming_calcs %>% filter(time_fct == "4") %>% 
  ggplot(aes(x = treatment, y= soc_isoC )) + geom_boxplot() +
  facet_grid(~plant, labeller = labeller(plant = plant.labs))+
  stat_compare_means(method = "t.test") +
  plot_theme + theme_bw()+
  theme(strip.text.x = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/soc_isoC.png",
      plot= plot_socisoC, dpi = 300, width = 8, height = 5, units = "in")

plant_socisoC <- priming_calcs %>% filter(time_fct == "4") %>% 
  ggplot(aes(x = plant, y= soc_isoC )) + geom_boxplot() +
  facet_grid(~treatment, labeller = labeller(treatment = tmt.labs))+
  stat_compare_means(method = "t.test") +
  plot_theme + theme_bw()+
  theme(strip.text.x = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/soc_isoC_plant.png",
      plot= plant_socisoC, dpi = 300, width = 8, height = 5, units = "in")

plot_doc <- priming_calcs %>% filter(time_fct == "4") %>% 
  ggplot(aes(x = treatment, y= doc_ugC )) + geom_boxplot() +
  facet_grid(~plant, labeller = labeller(plant = plant.labs))+
  stat_compare_means(method = "t.test") +
  plot_theme + theme_bw()+
  theme(strip.text.x = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/doc_ugC.png",
      plot= plot_doc, dpi = 300, width = 8, height = 5, units = "in")


plot_docisoC <- priming_calcs %>% filter(time_fct == "4") %>% 
  ggplot(aes(x = treatment, y= doc_isoC )) + geom_boxplot() +
  facet_grid(~plant, labeller = labeller(plant = plant.labs))+
  stat_compare_means(method = "t.test") +
  plot_theme + theme_bw()+
  theme(strip.text.x = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/doc_isoC.png",
      plot= plot_docisoC, dpi = 300, width = 8, height = 5, units = "in")

plant_docisoC <- priming_calcs %>% filter(time_fct == "4") %>% 
  ggplot(aes(x = plant, y= doc_isoC )) + geom_boxplot() +
  facet_grid(~treatment, labeller = labeller(treatment = tmt.labs))+
  stat_compare_means(method = "t.test") +
  plot_theme + theme_bw()+
  theme(strip.text.x = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/doc_isoC_plant.png",
      plot= plant_docisoC, dpi = 300, width = 8, height = 5, units = "in")

plot_whc <- priming_calcs %>% filter(time_fct == "4") %>% 
  ggplot(aes(x = treatment, y= whc )) + geom_boxplot() +
  facet_grid(~plant, labeller = labeller(plant = plant.labs))+
  stat_compare_means(method = "t.test") +
  plot_theme + theme_bw()+
  theme(strip.text.x = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/whc.png",
      plot= plot_whc, dpi = 300, width = 8, height = 5, units = "in")

plot_ugCgSoil <- priming_calcs %>% filter(time_fct == "4") %>% 
  ggplot(aes(x = treatment, y= ugC_gSoil )) + geom_boxplot() +
  facet_grid(~plant, labeller = labeller(plant = plant.labs))+
  stat_compare_means(method = "t.test") +
  plot_theme + theme_bw()+
  theme(strip.text.x = element_text(size = 12, face = "bold.italic")) + 
  ylab("ug C per g Soil from Amendment")

ggsave(filename = "../figures/ugCgSoil.png",
      plot= plot_ugCgSoil, dpi = 300, width = 8, height = 5, units = "in")

plot_ugNgSoil <- priming_calcs %>% filter(time_fct == "4") %>% 
  ggplot(aes(x = treatment, y= ugN_gSoil )) + geom_boxplot() +
  facet_grid(~plant, labeller = labeller(plant = plant.labs))+
  stat_compare_means(method = "t.test") +
  plot_theme + theme_bw()+
  theme(strip.text.x = element_text(size = 12, face = "bold.italic")) + 
  ylab("ug N per g Soil from Amendment")

ggsave(filename = "../figures/ugNgSoil.png",
      plot= plot_ugNgSoil, dpi = 300, width = 8, height = 5, units = "in")

```


Soil respired CO2-13C

```{r, echo = FALSE, warning = FALSE, message = FALSE}

plot_ctrl_soil_isoC <- priming_calcs %>% filter( between(ctrl_soil.isoC, -30, 0)) %>% 
  ggplot(aes(x= time_fct, y= ctrl_soil.isoC, fill = treatment)) + geom_boxplot() +
  facet_grid(plant~., labeller = labeller(plant = plant.labs)) +
  scale_y_continuous(limits = c(-35,5))+
  scale_fill_manual(name= "Treatment",
                      values = c("#66c2a5","#fc8d62"),
                    labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  xlab("Hours")+ ylab(expression(bold(paste(SOC~delta^{13},'C (‰)'))))+
  stat_compare_means(aes(label = ..p.signif..),
                  method = "t.test", label.y = 3)+
  plot_theme + theme_bw()+
  theme(strip.text.y = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/ctrl_soil_isoC.png",
      plot= plot_ctrl_soil_isoC, dpi = 300, width = 10, height = 5, units = "in")

plant_ctrl_soil_isoC <- priming_calcs %>% filter( between(ctrl_soil.isoC, -30, 0)) %>% 
  ggplot(aes(x= time_fct, y= ctrl_soil.isoC, fill = plant)) + geom_boxplot() +
  facet_grid(treatment ~., labeller = labeller(treatment = tmt.labs)) +
  scale_y_continuous(limits = c(-35,5))+
  scale_fill_manual(name= "Cover Type",
                      values = c("#6699FF","#CC9900"),
                    labels = c("Interspace", "L. tridentata"))+
  xlab("Hours")+ ylab(expression(bold(paste(SOC~delta^{13},'C (‰)'))))+
  stat_compare_means(aes(label = ..p.signif..),
                  method = "t.test", label.y = 3)+
  plot_theme + theme_bw()+
  theme(strip.text.y = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/ctrl_soil_isoC_plant.png",
      plot= plant_ctrl_soil_isoC, dpi = 300, width = 10, height = 5, units = "in")



```


Respiration Rate Over Time

```{r, echo = FALSE,warning = FALSE, message = FALSE}


plot_respC_time <- mean_mineralization %>% filter(response == "resp.C") %>% 
  ggplot(aes(x= time_num, y= mean, color= treatment)) + 
  geom_point(position=position_dodge(2), size= 1) +
  geom_errorbar(aes(ymin= mean - se, ymax= mean + se, 
                    colour= treatment), 
                width= 0, position=position_dodge(2)) +
  geom_path(aes(group = treatment, color = treatment))+
  facet_grid(plant~ amendment, labeller = labeller(plant = plant.labs, amendment = amend.labs)) +
  ylab(expression(paste(Respiration~(mu~g~CO[2]-C)))) +
  xlab("Hours")+
  scale_color_manual(name= "Treatment",
                    values = c("#66c2a5","#fc8d62"),
                    labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  scale_x_continuous(limits= c(0, 175), breaks = c(0,24,48,72,96,120,144,168))+
  theme_bw() + plot_theme + theme(axis.text.x = element_text(size=14)) +
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/respC_time.png",
      plot= plot_respC_time, dpi = 300, width = 8, height = 4, units = "in")

plant_respC_rate <- mean_mineralization %>% filter(response == "resp.hr") %>% 
  ggplot(aes(x= time_num, y= mean, color= treatment)) + 
  geom_point(position=position_dodge(2), size = 1) +
  geom_errorbar(aes(ymin= mean - se, ymax= mean + se, 
                    colour= treatment), 
                position=position_dodge(2), 
                width = 0) +
  geom_path(aes(group = treatment, color = treatment))+
  facet_grid(plant ~ amendment, 
             labeller = labeller(plant = plant.labs, amendment = amend.labs)) +
  ylab(expression(paste(Respiration~Rate~(mu~g~CO[2]-C~"*"~hr^-1)))) +
  xlab("Hours") +
  scale_color_manual(name= "Treatment",
                    values = c("#66c2a5","#fc8d62"),
                    labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  scale_x_continuous(limits= c(0, 175), breaks = c(0,24,48,72,96,120,144,168))+
  theme_bw() + plot_theme + theme(axis.text.x = element_text(size=14)) +
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/respC_rate.png",
      plot= plant_respC_rate, dpi = 300, width = 8, height = 4, units = "in")

```


Mineralization and Mineralization Rate Over Time

```{r, echo = FALSE, warning = FALSE, message = FALSE}

plot_min <- mean_mineralization %>% filter(response == "mineralization.C") %>% 
  ggplot(aes(x= time_num, y= mean, color= treatment)) + 
  geom_point(position=position_dodge(2), size=1) +
  geom_errorbar(aes(ymin= mean - se, ymax= mean + se, 
                    colour= treatment), 
                width=0, position=position_dodge(2)) +
  geom_path(aes(group = treatment, color = treatment))+
  facet_grid(plant ~ amendment, labeller = labeller(plant = plant.labs, amendment = amend.labs)) +
  ylab(expression(paste(Mineralization~(mu~g~CO[2]-C~"*"~mg~Soil-C^-1)))) +
  xlab("Hours") +
  scale_color_manual(name= "Treatment",
                    values = c("#66c2a5","#fc8d62"),
                    labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  plot_theme + theme_bw() +
  scale_x_continuous(limits= c(0, 175), breaks = c(0,24,48,72,96,120,144,168))+
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/mineralization.png",
      plot= plot_min, dpi = 300, width = 8, height = 4, units = "in")

plot_min_rate <- mean_mineralization %>% filter(response == "mineralization.hr") %>% 
  ggplot(aes(x= time_num, y= mean, color= treatment)) + 
  geom_point(position=position_dodge(4), size= 1) +
  geom_errorbar(aes(ymin= mean - se, ymax= mean + se, 
                    colour= treatment), 
                width=0 , position=position_dodge(4)) +
  geom_path(aes(group = treatment, color = treatment))+
  facet_grid(plant~ amendment, labeller = labeller(plant = plant.labs, amendment = amend.labs)) +
  ylab(expression(paste(Mineralization~(mu~g~CO[2]-C~"*"~mg~Soil-C^-1~"*"~hr^-1)))) +
  xlab("Hours") +
  scale_color_manual(name= "Treatment",
                      values = c("#66c2a5","#fc8d62"),
                    labels = c(expression(paste("Ambient")),expression("+CO"[2],)))+
  plot_theme + theme_bw() +
  scale_x_continuous(limits= c(0, 175), breaks = c(0,24,48,72,96,120,144,168))+
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/mineralization_rate.png",
      plot= plot_min_rate, dpi = 300, width = 8, height = 4, units = "in")


cumu_min <- cumu_resp_long %>% filter(time_fct == "168") %>% 
  ggplot(aes(x= plant, y = cumu.mineralization.C, fill= treatment)) + geom_boxplot()+
  facet_grid(~ amendment, labeller = labeller(amendment = amend.labs)) +
  ylab(expression(atop("Cumulative Mineralization",(mu~g~CO[2]-C~"*"~mg~Soil-C^-1)))) +
  scale_x_discrete(labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  xlab(element_blank())+
  scale_fill_manual(name= "Treatment",
                    values = c("#66c2a5","#fc8d62"),
                    labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  theme_bw() + plot_theme +
  theme(strip.text.x = element_text(size = 12, face = "bold"))
  

ggsave(filename = "../figures/cumu_mineralization.png",
      plot= cumu_min, dpi = 300, width = 8, height = 4, units = "in")


# Mineralization by cover type
plant_min <- mean_mineralization %>% filter(response == "mineralization.C") %>% 
  ggplot(aes(x= time_num, y= mean, color= plant)) + 
  geom_point(position=position_dodge(2), size=1) +
  geom_errorbar(aes(ymin= mean - se, ymax= mean + se, 
                    colour= plant), 
                width=0, position=position_dodge(2)) +
  geom_path(aes(group = plant, color = plant))+
  facet_grid(treatment ~ amendment, labeller = labeller(treament = tmt.labs, amendment = amend.labs)) +
  ylab(expression(paste(Mineralization~(mu~g~CO[2]-C~"*"~mg~Soil-C^-1)))) +
  xlab("Hours") +
  scale_color_manual(name= "Cover Type",
                      values = c("#6699FF","#CC9900"),
                    labels = c("Interspace", "L. tridentata"))+
  theme_bw() + plot_theme + 
  scale_x_continuous(limits= c(0, 175), breaks = c(0,24,48,72,96,120,144,168))+
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold"))

ggsave(filename = "../figures/mineralization_plant.png",
      plot= plant_min, dpi = 300, width = 8, height = 4, units = "in")

```

Relative primed ug C

```{r, echo = FALSE}

rel_primed <- abs_cumu_resp_long %>% filter(time_fct == "168") %>% filter(amendment == "glu") %>% 
  ggplot(aes(x = plant, y = cumu.rel.primed.ugC, fill= treatment)) + geom_boxplot() +
  stat_compare_means(method = "t.test", label.y = 500) +
  ylab(expression(atop("Relative Primed C",(mu~g~Primed~C~"*"~mg~SOC^-1)))) +
  xlab(element_blank())+
  scale_x_discrete(labels = c("Interspace", "L. tridentata"))+
  scale_fill_manual(name= "Treatment",
                    values = c("#66c2a5","#fc8d62"),
                    labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  theme_bw() + plot_theme+
  theme(strip.text.x = element_text(size = 12, face = "bold"))

ggsave(filename = "../figures/rel_primed.png",
      plot= rel_primed, dpi = 300, width = 6, height = 4, units = "in")


rel_primed_plant <- abs_cumu_resp_long %>% filter(time_fct == "168") %>% filter(amendment == "glu") %>% 
  ggplot(aes(x = treatment, y = cumu.rel.primed.ugC, fill= plant)) + geom_boxplot() +
  stat_compare_means(method = "t.test", label.y = 500) +
  ylab(expression(atop("Relative Primed C",(mu~g~Primed~C~"*"~mg~SOC^-1)))) +
  scale_x_discrete(labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  xlab(element_blank())+
  scale_fill_manual(name= "Cover Type",
                      values = c("#6699FF","#CC9900"),
                    labels = c("Interspace", "L. tridentata"))+
  theme_bw() + plot_theme +
  theme(strip.text.x = element_text(size = 12, face = "bold"))  

ggsave(filename = "../figures/rel_primed_plant.png",
      plot= rel_primed_plant, dpi = 300, width = 6, height = 4, units = "in")


```



Cumulative Soil Derived CO2-C over time (Control v Glutamic Acid)

```{r, echo = FALSE, warning = FALSE, message = FALSE}

cumu.soil.ugC <- lineplot_data %>% filter(Csource == "cumu.soil.ugC") %>% 
  ggplot(aes(x= time_num, y= mean, color= treatment)) + 
  geom_point(position=position_dodge(4), size= 1) +
  geom_errorbar(aes(ymin= mean - se, ymax= mean + se, 
                    colour= treatment), 
                width=0, position=position_dodge(4)) +
  geom_path(aes(group = treatment, color = treatment) )+
  facet_grid(plant~ amendment, labeller = labeller(plant = plant.labs, amendment = amend.labs)) + 
  ylab(expression(paste(Cumulative~Soil~Derived~CO[2]-C~(mu~g))))+ 
  xlab("Hours")+
  scale_color_manual(name = (expression(paste(CO[2]~Treatment))), 
                   values = c("#66c2a5","#fc8d62"), 
                   labels=c("Control",expression(paste(+CO[2]))))+
  scale_x_continuous(limits= c(0, 175), breaks = c(0,24,48,72,96,120,144,168))+
  theme_bw() + plot_theme + 
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/cumu.soil.ugC.png",
      plot= cumu.soil.ugC, dpi = 300, width = 8, height = 4, units = "in")

```

Priming over time with negative priming

```{r, echo = FALSE}
neg_priming <- priming_calcs %>% filter(between(glu_primed.ugC, -200, 300)) %>% 
  ggplot(aes(x= time_fct, y= glu_primed.ugC, fill = treatment)) + geom_boxplot() +
  facet_grid(~plant,labeller = labeller(plant = plant.labs)) +
  ylab(expression(paste(Primed~C~(mu~g~CO[2]-C)))) +
  xlab("Hours") +
  scale_fill_manual(name= "Treatment",
                    values = c("#66c2a5","#fc8d62"),
                    labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  theme_bw() + plot_theme +
  theme(strip.text.x = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/neg_priming.png",
      plot= neg_priming, dpi = 300, width = 10, height = 4, units = "in")
```


Respired C Source over time
"Base" Respiration is the control (+H2O) respiration.
Base + primed = total soil derived CO2
Base + primed + amendment = total CO2 respired 

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 15}

mean_baseC_data$Csource = factor(mean_baseC_data$Csource, 
                                 c("cumu.amend.ugC", "cumu.primed.ugC", "cumu.base.ugC"))

resp_Csource_all <- mean_baseC_data %>% 
  ggplot(aes(y= mean, x= treatment, fill = Csource))+
  geom_bar(position="stack", stat="identity") +
  facet_grid(plant~time_fct,labeller = labeller(plant = plant.labs, amendment = amend.labs))+
  ylab(expression(paste(Cumulative~CO[2]-C~(mu~g))))+ 
  scale_x_discrete(labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  scale_fill_manual(name = expression(paste(Source~of~CO[2])),
                    label = c("Amendment", "Primed", "Base"),
                      values = c("#66c2a5","#fc8d62","#8da0cb"))+
  scale_y_continuous(expand = c(0,0), limits = c(0,1750))+
  xlab(element_blank())+
   theme_bw()+ plot_theme +
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/resp_Csource_all.png",
      plot= resp_Csource_all, dpi = 300, width = 13, height = 6, units = "in")

resp_soilC <- mean_baseC_data %>% filter(!grepl("amend", Csource)) %>% 
  ggplot(aes(x= treatment, y= mean, fill = Csource))+
  geom_bar( stat="identity") +
  facet_grid(plant ~ time_fct,
             labeller = labeller(plant = plant.labs, amendment = amend.labs))+
  ylab(expression(paste(Cumulative~Soil~Derived~CO[2]-C~(mu~g))))+ 
  scale_x_discrete(labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  scale_fill_manual(name = expression(paste(Source~of~CO[2])),
                    label = c("Primed","Base"),
                      values = c("#fc8d62","#8da0cb"))+
  scale_y_continuous(expand = c(0,0), limits = c(0,1400))+
  xlab(element_blank())+
  plot_theme + theme_bw()+
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic")) 

ggsave(filename = "../figures/resp_soilC.png",
      plot= resp_soilC, dpi = 300, width = 10, height = 6, units = "in")

resp_amend <- mean_baseC_data %>% filter(Csource == "cumu.amend.ugC") %>% 
  ggplot(aes(y= mean, x= treatment, fill = Csource))+
  geom_bar( stat="identity" ) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                  width=.2, position=position_dodge(.9))+
  facet_grid(plant~time_fct,labeller = labeller(plant = plant.labs, amendment = amend.labs))+
  ylab(expression(paste(Cumulative~Amendment~CO[2]-C~(mu~g))))+ 
  scale_x_discrete(labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  scale_fill_manual(values = c("#66c2a5"))+
  scale_y_continuous(expand = c(0,0), limits = c(0,450))+
  xlab(element_blank())+
  plot_theme + theme_bw()+
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic")) +
    theme(legend.position = "none")

ggsave(filename = "../figures/resp_amend.png",
      plot= resp_amend, dpi = 300, width = 8, height = 4, units = "in")

resp_base <- mean_baseC_data %>% filter(Csource == "cumu.base.ugC") %>% 
  ggplot(aes(y= mean, x= treatment, fill = Csource))+
  geom_bar(stat="identity") + 
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se, fill = Csource),
                  width=.2, position=position_dodge(.9))+
  facet_grid(plant~time_fct,labeller = labeller(plant = plant.labs, amendment = amend.labs))+
  ylab(expression(paste(Cumulative~Base~CO[2]-C~(mu~g))))+ 
  scale_x_discrete(labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  scale_fill_manual(values = c("#fc8d62"))+
  scale_y_continuous(expand = c(0,0), limits = c(0,1350))+
  xlab(element_blank())+
  plot_theme + theme_bw()+
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic")) +
    theme(legend.position = "none")

ggsave(filename = "../figures/resp_base.png",
      plot= resp_base, dpi = 300, width = 8, height = 4, units = "in")

resp_primed <- mean_baseC_data %>% filter(Csource == "cumu.primed.ugC") %>% 
  ggplot(aes(y= mean, x= treatment, fill = Csource))+
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se, fill = Csource),
                  width=.2, position=position_dodge(.9))+
  facet_grid(plant~time_fct,labeller = labeller(plant = plant.labs, amendment = amend.labs))+
  ylab(expression(paste(Cumulative~Primed~CO[2]-C~(mu~g))))+ 
  scale_x_discrete(labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  scale_fill_manual(values = c("#8da0cb"))+
  theme(legend.position = element_blank())+
  scale_y_continuous(expand = c(0,0), limits = c(0,350))+
  xlab(element_blank())+
  plot_theme + theme_bw()+
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic")) +
    theme(legend.position = "none")

ggsave(filename = "../figures/resp_primed.png",
      plot= resp_primed, dpi = 300, width = 8, height = 4, units = "in")

```


Bar plots cumulative to 168 hrs 

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width= 15}

p1 <- mean_baseC_data %>% filter(time_fct == "168") %>% 
  ggplot(aes(y= mean, x= treatment, fill = Csource))+
  geom_bar(position=position_stack(reverse = TRUE), stat="identity") +
  facet_grid(~plant,labeller = labeller(plant = plant.labs, amendment = amend.labs))+
  ylab(expression(paste(Cumulative~Soil~Derived~CO[2]-C~(mu~g))))+ 
  scale_x_discrete(labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  scale_fill_manual(name = expression(paste(Source~of~CO[2])),
                    label = c("Amendment", "Base", "Primed"),
                      values = c("#66c2a5","#fc8d62","#8da0cb"))+
  scale_y_continuous(expand = c(0,0), limits = c(0,1750))+
  xlab(element_blank())+
  theme_bw() +  plot_theme + 
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic")) +
  theme(legend.position = "bottom")

ggsave(filename = "../figures/cumu_ugC_168.png",
      plot= p1, dpi = 300, width = 6, height = 6, units = "in")

p2 <- mean_baseC_data %>% filter(time_fct == "168") %>% 
  filter(!grepl("amend", Csource)) %>% 
  ggplot(aes(x= treatment, y= mean, fill = Csource))+
  geom_bar(position=position_stack(reverse = TRUE), stat="identity") +
  facet_grid(~plant,
             labeller = labeller(plant = plant.labs, amendment = amend.labs))+
  ylab(expression(paste(Cumulative~Soil~Derived~CO[2]-C~(mu~g))))+ 
  scale_x_discrete(labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  scale_fill_manual(name = expression(paste(Source~of~CO[2])),
                    label = c( "Base", "Primed"),
                      values = c("#fc8d62","#8da0cb"))+
  scale_y_continuous(expand = c(0,0), limits = c(0,1750))+
  xlab(element_blank())+
  theme_bw() +  plot_theme +
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic")) +
  theme(legend.position = "bottom")

ggsave(filename = "../figures/cumu_soil_168.png",
      plot= p2, dpi = 300, width = 6, height = 6, units = "in")


p3 <- mean_baseC_data %>% filter(time_fct == "168") %>% 
  filter(Csource == "cumu.amend.ugC") %>% 
  ggplot(aes(y= mean, x= treatment, fill = Csource))+
  geom_bar( stat="identity") +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se, fill = Csource),
                  width=.2, position=position_dodge(.9))+
  facet_grid(~plant,labeller = labeller(plant = plant.labs, amendment = amend.labs))+
  ylab(expression(paste(Cumulative~Amendment~CO[2]-C~(mu~g))))+ 
  scale_x_discrete(labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  scale_fill_manual(name = expression(paste(Source~of~CO[2])),
                    label = c("Base"),
                      values = c("#66c2a5"))+
  theme(legend.position = "none")+
  scale_y_continuous(expand = c(0,0), limits = c(0,1350))+
  xlab(element_blank())+
   theme_bw() +  plot_theme +
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic")) +
  theme(legend.position = "bottom")

ggsave(filename = "../figures/cumu_amend_168.png",
      plot= p3, dpi = 300, width = 6, height = 6, units = "in")

p4 <- mean_baseC_data %>% filter(time_fct == "168") %>% 
  filter(Csource == "cumu.base.ugC") %>% 
  ggplot(aes(y= mean, x= treatment, fill = Csource))+
  geom_bar(stat="identity") + 
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se, fill = Csource),
                  width=.2, position=position_dodge(.9))+
  facet_grid(~plant,labeller = labeller(plant = plant.labs, amendment = amend.labs))+
  ylab(expression(paste(Cumulative~Base~CO[2]-C~(mu~g))))+ 
  scale_x_discrete(labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  scale_fill_manual(name = expression(paste(Source~of~CO[2])),
                    label = c("Base"),
                      values = c("#fc8d62"))+
  theme(legend.position = "none")+
  scale_y_continuous(expand = c(0,0), limits = c(0,1350))+
  xlab(element_blank())+
   theme_bw() +  plot_theme +
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic")) +
  theme(legend.position = "bottom")

ggsave(filename = "../figures/cumu_base_168.png",
      plot= p4, dpi = 300, width = 6, height = 6, units = "in")

p5 <- mean_baseC_data %>% filter(time_fct == "168") %>% 
  filter(Csource == "cumu.primed.ugC") %>% 
  ggplot(aes(y= mean, x= treatment, fill = Csource))+
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se, fill = Csource),
                  width=.2, position=position_dodge(.9))+
  facet_grid(~plant,labeller = labeller(plant = plant.labs, amendment = amend.labs))+
  ylab(expression(paste(Cumulative~Primed~CO[2]-C~(mu~g))))+ 
  scale_x_discrete(labels = c(expression(paste("Control")),expression("+CO"[2],)))+
  scale_fill_manual(name = expression(paste(Source~of~CO[2])),
                    label = c("Primed"),
                      values = c("#8da0cb"))+
  theme(legend.position = element_blank())+
  scale_y_continuous(expand = c(0,0), limits = c(0,1350))+
  theme(legend.position = "none")+
  xlab(element_blank())+
   theme_bw() +  plot_theme +
  theme(strip.text.x = element_text(size = 12, face = "bold.italic")) +
  theme(legend.position = "bottom")

ggsave(filename = "../figures/cumu_primed_168.png",
      plot= p5, dpi = 300, width = 6, height = 6, units = "in")

p6 <- ggarrange(p1, p3, p4, p5, common.legend = TRUE, legend = "bottom")
ggsave(filename = "../figures/all_168.png",
      plot= p6, dpi = 300, width = 10, height = 8, units = "in")

```


DOC relationship with respired C
Strong relationship between DOC and control respiration (except for LATR eCO2)
Weaker relationship between DOC and glutatmic acid soil resp or primed C 


```{r, echo = FALSE, warning = FALSE, message = FALSE}

doc_ctrl <- resp_cumu %>% 
  ggplot(aes(x = doc_ugC, y = ctrl_cumu.soil.ugC, group = treatment, color= treatment)) + 
  geom_point() + 
  geom_smooth(method= "lm", se= TRUE, fullrange= TRUE, alpha = 0.3)+ 
  stat_cor(method="spearman", label.y = c(2700, 3000), 
           size= 3, r.accuracy = 0.01, p.accuracy =0.01) + 
  facet_grid(plant~time_fct, labeller= labeller(plant = plant.labs)) +
  ylab(expression(paste(Control~Cumulative~Soil~Derived~CO[2]-C~(mu~g))))+
  xlab(expression(paste(Dissolved~Organic~C~(mu~g~C~"*"~g~Soil^-1)))) +
  scale_color_manual(name = expression(paste(CO[2]~Treatment)),
                    label = c("Ambient", expression(paste(+CO[2]))),
                      values = c("#66c2a5","#fc8d62"))+
  plot_theme + theme_bw() + theme(legend.position = "bottom")+
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/corr_doc_ctrl.png",
      plot= doc_ctrl, dpi = 300, width = 10, height = 6, units = "in")

resp_cumu %>% 
  ggplot(aes(x = doc_ugC, y = ctrl_cumu.soil.ugC, group = treatment, color= treatment)) + 
  geom_point() + ggtitle("Control Soil") + 
  geom_smooth(method= "lm", se= TRUE, fullrange= TRUE, alpha = 0.3)+ 
  stat_cor(method="spearman", label.y = c(2700, 3000), 
           size= 3, r.accuracy = 0.01, p.accuracy =0.01) + 
  facet_grid(~time_fct) +
  ylab(expression(paste(Cumulative~Soil~Derived~CO[2]-C~(mu~g))))+
  xlab(expression(paste(Dissolved~Organic~C~(mu~g~C~"*"~g~Soil^-1)))) +
  scale_color_manual(name = expression(paste(CO[2]~Treatment)),
                    label = c("Ambient", expression(paste(+CO[2]))),
                      values = c("#66c2a5","#fc8d62"))+
  plot_theme + theme_bw()+ theme(legend.position = "bottom")+
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic"))


doc_glu <- resp_cumu %>% 
  ggplot(aes(x = doc_ugC, y = glu_cumu.soil.ugC, group = treatment, color= treatment)) + 
  geom_point() +  
  geom_smooth(method= "lm", se= TRUE, fullrange= TRUE, alpha = 0.3)+ 
  stat_cor(method="spearman", label.y = c(3000, 3200), 
           size= 3, r.accuracy = 0.01, p.accuracy =0.01) +
  theme(legend.position = "bottom")+
  facet_grid(plant~time_fct, labeller= labeller(plant = plant.labs)) +
  ylab(expression(paste(Glutamic~Acid~Cumulative~Soil~Derived~CO[2]-C~(mu~g))))+
  xlab(expression(paste(Dissolved~Organic~C~(mu~g~C~"*"~g~Soil^-1)))) +
  scale_color_manual(name = expression(paste(CO[2]~Treatment)),
                    label = c("Ambient", expression(paste(+CO[2]))),
                      values = c("#66c2a5","#fc8d62"))+
  plot_theme + theme_bw() + theme(legend.position = "bottom")+
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/corr_doc_glu.png",
      plot= doc_glu, dpi = 300, width = 10, height = 6, units = "in")


resp_cumu %>% 
  ggplot(aes(x = doc_ugC, y = glu_cumu.soil.ugC, group = treatment, color= treatment)) + 
  geom_point() + ggtitle("Glutamic Acid Soil") + 
  geom_smooth(method= "lm", se= TRUE, fullrange= TRUE, alpha = 0.3)+ 
  stat_cor(method="spearman", label.y = 2000) + 
  facet_grid(~time_fct) +
  ylab(expression(paste(Cumulative~Soil~Derived~CO[2]-C~(mu~g))))+
  xlab(expression(paste(Dissolved~Organic~C~(mu~g~C~"*"~g~Soil^-1)))) +
  scale_color_manual(name = expression(paste(CO[2]~Treatment)),
                    label = c("Ambient", expression(paste(+CO[2]))),
                      values = c("#66c2a5","#fc8d62"))+
  plot_theme + theme_bw()+ theme(legend.position = "bottom")+
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic"))


doc_primed <- resp_cumu %>% 
  ggplot(aes(x = doc_ugC, y = glu_cumu.primed.ugC, group = treatment, color= treatment)) + 
  geom_point() + 
  geom_smooth(method= "lm", se= TRUE, fullrange= TRUE, alpha = 0.3)+ 
  stat_cor(method="spearman", label.y = c(1400, 1600), 
           size= 3, r.accuracy = 0.01, p.accuracy =0.01) +
  facet_grid(plant~time_fct, labeller= labeller(plant = plant.labs)) +
  ylab(expression(paste(Cumulative~Primed~CO[2]-C~(mu~g))))+
  xlab(expression(paste(Dissolved~Organic~C~(mu~g~C~"*"~g~Soil^-1)))) +
  scale_color_manual(name = expression(paste(CO[2]~Treatment)),
                    label = c("Ambient", expression(paste(+CO[2]))),
                     values = c("#66c2a5","#fc8d62"))+
  plot_theme + theme_bw()+ theme(legend.position = "bottom")+
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic"))

ggsave(filename = "../figures/corr_doc_primed.png",
      plot= doc_primed, dpi = 300, width = 10, height = 6, units = "in")

resp_cumu %>% filter(between(ctrl_soil.isoC, -30,0)) %>% 
  ggplot(aes(x = doc_isoC, y = ctrl_soil.isoC, group = treatment, color= treatment)) + 
  geom_point() +
  geom_smooth(method= "lm", se= TRUE, fullrange= TRUE, alpha = 0.3)+ 
  stat_cor(method="spearman") + 
  facet_grid(~time_fct) +
  #ylab(expression(paste(Cumulative~Primed~CO[2]-C~(mu~g))))+
  #xlab(expression(paste(Dissolved~Organic~C~(mu~g~C~"*"~g~Soil^-1)))) +
  scale_color_manual(name = expression(paste(CO[2]~Treatment)),
                    label = c("Ambient", expression(paste(+CO[2]))),
                      values = c("#6699FF","#CC9900"))+
  plot_theme + theme_bw()+ theme(legend.position = "bottom")+
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 12, face = "bold.italic"))


```


Potentially useful other comparisons

```{r, echo = FALSE, warning = FALSE, message = FALSE}

resp_cumu %>% ggplot(aes(time_fct, y= ctrl_soil.ugC, fill = treatment)) + 
  geom_boxplot() +
  facet_grid(~plant) + stat_compare_means(aes(label = ..p.signif..),
                  method = "anova", label.y = 500)

resp_cumu %>% ggplot(aes(time_fct, y= ctrl_soil.ugC.hr, fill = treatment)) + 
  geom_boxplot() +
  facet_grid(~plant) + stat_compare_means(aes(label = ..p.signif..),
                  method = "anova", label.y = 50)

resp_cumu %>% ggplot(aes(time_fct, y= glu_soil.ugC, fill = treatment)) + 
  geom_boxplot() +
  facet_grid(~plant) + stat_compare_means(aes(label = ..p.signif..),
                  method = "anova", label.y = 600)

resp_cumu %>% ggplot(aes(time_fct, y= glu_soil.ugC.hr, fill = treatment)) + 
  geom_boxplot() +
  facet_grid(~plant) + stat_compare_means(aes(label = ..p.signif..),
                  method = "anova", label.y = 50)

resp_cumu %>% ggplot(aes(time_fct, y= glu_cumu.amend.ugC, fill = treatment)) + 
  geom_boxplot() +
  facet_grid(~plant) + stat_compare_means(aes(label = ..p.signif..),
                  method = "anova", label.y = 500)

resp_cumu %>% ggplot(aes(time_fct, y= glu_primed.ugC, fill = treatment)) + 
  geom_boxplot() +
  facet_grid(~plant) + stat_compare_means(aes(label = ..p.signif..),
                  method = "anova", label.y = 200)



```