---
title: "Stats"
author: "Kelsey Jensen"
date: "3/7/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(tidyverse)
library(ggpubr)
library(lme4)
library(lmerTest)
library(emmeans)

load("../data/priming_calcs.RData")
load("../data/cumu_resp_long.RData")

```

SOC, DOC, WHC
```{r, echo = FALSE}
soil.char <- cumu_resp_long %>% filter(time_fct == "4") %>% filter(amendment == "ctrl")

# SOC
lm1 <- lmer(log(soc_mgC) ~ (plant*treatment)^2 + (1|ring), data = soil.char)
summary(lm1)
anova(lm1)

plot(predict(lm1), residuals(lm1)) 
qqnorm(residuals(lm1)); qqline(residuals(lm1))
hist(residuals(lm1))

summary(emmeans(lm1, pairwise ~ treatment|plant)$contrasts)
summary(emmeans(lm1, pairwise ~ plant|treatment)$contrasts)

summary(emmeans(lm1,  ~treatment|plant), type= "response")

# DOC
lm2 <- lmer(doc_ugC ~ (plant*treatment)^2 + (1|ring), data = soil.char)
summary(lm2)
anova(lm2)

plot(predict(lm2), residuals(lm2)) 
qqnorm(residuals(lm2)); qqline(residuals(lm2))
hist(residuals(lm2))

summary(emmeans(lm2, pairwise ~ treatment|plant)$contrasts)
summary(emmeans(lm2, pairwise ~ plant|treatment)$contrasts)

summary(emmeans(lm2,  ~treatment + plant), type= "response")
summary(emmeans(lm2,  ~ plant), type= "response")

# WHC
lm3 <- lmer(whc ~ (plant*treatment)^2 + (1|ring), data = soil.char)
summary(lm3)
anova(lm3)

plot(predict(lm3), residuals(lm3)) 
qqnorm(residuals(lm3)); qqline(residuals(lm3))
hist(residuals(lm3))

summary(emmeans(lm3, pairwise ~ plant)$contrasts)
summary(emmeans(lm3, pairwise ~ plant|treatment)$contrasts)
summary(emmeans(lm3,  ~ plant), type= "response")

# SOC 13C
lm4 <- lmer(soc_isoC ~ (plant*treatment)^2 + (1|ring), data = soil.char)
summary(lm4)
anova(lm4)

plot(predict(lm4), residuals(lm4)) 
qqnorm(residuals(lm4)); qqline(residuals(lm4))
hist(residuals(lm4))

summary(emmeans(lm4, pairwise ~ treatment|plant)$contrasts)
summary(emmeans(lm4, pairwise ~ plant|treatment)$contrasts)


# DOC 13C
lm5 <- lmer(doc_isoC ~ (plant*treatment)^2 + (1|ring), data = soil.char)
summary(lm5)
anova(lm5)

plot(predict(lm5), residuals(lm5)) 
qqnorm(residuals(lm5)); qqline(residuals(lm5))
hist(residuals(lm5))

summary(emmeans(lm5, pairwise ~ treatment|plant)$contrasts)
summary(emmeans(lm5, pairwise ~ plant|treatment)$contrasts)
```


Assessing effect of glutamic C concentration on respiration
```{r, echo = FALSE}

lm.gluC <- lmer(sqrt(glu_soil.ugC) ~ (plant*treatment*time_fct)+(glu_ugC.gSoil) + 
              (1|ring) + (1|ID), data = priming_calcs)

plot(predict(lm.gluC), residuals(lm.gluC)) 
qqnorm(residuals(lm.gluC)); qqline(residuals(lm.gluC))
hist(residuals(lm.gluC))

summary(lm.gluC)
anova(lm.gluC)


lm.gluC2 <- lmer(sqrt(glu_soil.ugC.hr) ~ (plant*treatment*time_fct)+(glu_ugC.gSoil) + 
                (1|ring) + (1|ID), data = priming_calcs)

plot(predict(lm.gluC2), residuals(lm.gluC2)) 
qqnorm(residuals(lm.gluC2)); qqline(residuals(lm.gluC2))
hist(residuals(lm.gluC2))

summary(lm.gluC2)
anova(lm.gluC2)

# No effect of ugC_gSoil on rate or absolute resp

```


Respiration (rate)

```{r}

# Soil resp rate over time
lm6 <- lmer(sqrt(soil.ugC.hr) ~ (plant * treatment * amendment * time_fct)^4 + 
              (1|ring) + (1|ID) + (1|ID:amendment), data = cumu_resp_long) 
summary(lm6)
anova(lm6)

plot(predict(lm6), residuals(lm6)) # ok
qqnorm(residuals(lm6)); qqline(residuals(lm6)) # ok
hist(residuals(lm6)) # normal dist with sqrt

paircomp6 <- summary(emmeans(lm6, pairwise ~ treatment|plant|amendment|time_fct)$contrasts)
paircomp6.1 <- summary(emmeans(lm6, pairwise ~ plant|amendment|treatment|time_fct)$contrasts)
write.csv(paircomp6, "../output/paircomp_soilugChr.csv")

emmeans6 <- summary(emmeans(lm6,  ~treatment+plant+amendment+time_fct), type= "response")
write.csv(emmeans6, "../output/emmeans_soilugChr.csv")
```


Mineralization Rates 
```{r, echo = FALSE}

lm.min <- lmer(sqrt(mineralization.hr) ~ (plant * treatment * amendment * time_fct) + 
              (1|ring) + (1|ID) + (1|ID:amendment), data = cumu_resp_long)
summary(lm.min)
anova(lm.min)

plot(predict(lm.min), residuals(lm.min)) # ok
qqnorm(residuals(lm.min)); qqline(residuals(lm.min)) # ok
hist(residuals(lm.min)) # ok

paircomp.min <- summary(emmeans(lm.min, pairwise ~ treatment|plant|amendment|time_fct)$contrasts)

write.csv(paircomp.min, "../output/paircomp_min.csv")

emmeans.min <- summary(emmeans(lm.min,  ~treatment+amendment+plant+time_fct), type= "response")


```


Cumulative Resp
```{r, echo = FALSE}
cumu.4 <- cumu_resp_long %>% filter(time_num == 4)

# Cumulative soil resp 
lm7.1 <- lmer(sqrt(cumu.soil.ugC) ~ (plant * treatment * amendment) + 
              (1|ring) + (1|ID), data = cumu.4)

plot(predict(lm7.1), residuals(lm7.1)) # good
qqnorm(residuals(lm7.1)); qqline(residuals(lm7.1)) # good
hist(residuals(lm7.1)) # best with sqrt

summary(lm7.1)
anova(lm7.1)

paircomp7.1 <- summary(emmeans(lm7.1, pairwise ~ treatment|plant|amendment)$contrasts)

write.csv(paircomp7.1, "../output/paircomp_cumu.soilugC.4.csv")

emmeans7.1 <- summary(emmeans(lm7.1,  ~treatment + plant + amendment), type= "response")


## 168
cumu.168 <- cumu_resp_long %>% filter(time_fct == "168")

# Cumulative soil resp 
lm7.2 <- lmer(sqrt(cumu.soil.ugC) ~ (plant * treatment * amendment) + 
              (1|ring) + (1|ID), data = cumu.168)

plot(predict(lm7.2), residuals(lm7.2)) # good
qqnorm(residuals(lm7.2)); qqline(residuals(lm7.2)) # good
hist(residuals(lm7.2)) # best with sqrt

summary(lm7.2)
anova(lm7.2)

paircomp7.2 <- summary(emmeans(lm7.2, pairwise ~ treatment|plant|amendment)$contrasts)

write.csv(paircomp7.2, "../output/paircomp_cumu.soilugC.168.csv")

# Cumu amendment resp (Super not normal residuals)
hist(sqrt(cumu.168$cumu.amend.ugC))
lm7.3 <- lmer(sqrt(cumu.amend.ugC) ~ (plant * treatment * amendment) + 
              (1|ring) + (1|ID), data = cumu.168)

plot(predict(lm7.3), residuals(lm7.3)) # good
qqnorm(residuals(lm7.3)); qqline(residuals(lm7.3)) # good
hist(residuals(lm7.3)) 

```

Control soil isoC
```{r, echo = FALSE}

ctrl_soil_isoC <- priming_calcs %>% filter( between(ctrl_soil.isoC, -30, 0))

lm.isoC <- lmer(ctrl_soil.isoC ~ (plant * treatment *  time_fct) + 
              (1|ring) + (1|ID), data = ctrl_soil_isoC)

plot(predict(lm.isoC) , residuals(lm.isoC)) # good
qqnorm(residuals(lm.isoC )); qqline(residuals(lm.isoC )) # good
hist(residuals(lm.isoC )) # good

summary(lm.isoC)
anova(lm.isoC)

paircomp.isoC <- summary(emmeans(lm.isoC, pairwise ~ treatment|plant|time_fct)$contrasts)

write.csv(paircomp7.2, "../output/paircomp_cumu.soilugC.168.csv")

```


## Priming analysis
Priming rate
```{r, echo = FALSE}
primedC <- cumu_resp_long %>% filter(amendment == "glu")

lm8 <- lmer(sqrt(abs(primed.ugC.hr)) ~ (plant * treatment * time_fct) + 
              (1|ring) + (1|ID) + (1|ID:amendment), data = primedC) 
summary(lm8)
anova(lm8)

plot(predict(lm8), residuals(lm8)) # ok
qqnorm(residuals(lm8)); qqline(residuals(lm8)) # ok
hist(residuals(lm8)) # ok

paircomp8 <- summary(emmeans(lm8, pairwise ~ treatment|plant|time_fct)$contrasts)

#write.csv(paircomp8, "../output/paircomp_soilugChr.csv")

emmeans8 <- summary(emmeans(lm8,  ~treatment+plant+time_fct), type= "response")
# write.csv(emmeans8, "../output/emmeans_soilugChr.csv")

primedC %>% ggplot(aes(x = time_num, y= primed.ugC.hr, color = treatment)) + geom_point()
```

Priming Effect
```{r, echo = FALSE}
priming.effect.data <- cumu_resp_long %>% filter(priming.effect != Inf) %>% 
  filter(priming.effect <= 20) %>% filter(amendment =="glu") %>% filter(time_fct == "4")

lm.prime <- lmer(sqrt(priming.effect) ~ (treatment*plant) + 
              (1|ring), data = priming.effect.data)

plot(predict(lm.prime), residuals(lm.prime)) # ok
qqnorm(residuals(lm.prime)); qqline(residuals(lm.prime)) # ok
hist(residuals(lm.prime)) # not great

summary(lm.prime)
anova(lm.prime)

paircomp.p <- summary(emmeans(lm.prime, pairwise ~ treatment|plant)$contrasts)

emmeans.p <- summary(emmeans(lm.prime,  ~treatment+plant), type= "response")
```

Net priming at 4 and 168 hours
```{r, echo = FALSE}
# 4 hours
primed.4 <- cumu_resp_long %>% filter(time_fct == "4") %>% filter(amendment == "glu")

lm9 <- lmer(sqrt(cumu.primed.ugC) ~ (plant*treatment) + 
              (1|ring), data = primed.4) # sqrt and log transformations don't work great
summary(lm9)
anova(lm9)

plot(predict(lm9), residuals(lm9)) # ok
qqnorm(residuals(lm9)); qqline(residuals(lm9)) # ok
hist(residuals(lm9)) # ok but narrow

paircomp.9 <- summary(emmeans(lm9, pairwise ~ treatment|plant)$contrasts)
emmeans.9 <- summary(emmeans(lm9,  ~plant), type= "response")

# 168 Hours
primed.168 <- cumu_resp_long %>% filter(time_fct == "168") %>% filter(amendment == "glu")

lm10 <- lmer(sqrt(abs(cumu.primed.ugC)) ~ (plant*treatment) + 
              (1|ring), data = primed.168) # sqrt and log transformations don't work great
summary(lm10)
anova(lm10)

plot(predict(lm10), residuals(lm10))
qqnorm(residuals(lm10)); qqline(residuals(lm10)) 
hist(residuals(lm10)) # ok but narrow

paircomp.10 <- summary(emmeans(lm10, pairwise ~ treatment|plant)$contrasts)
emmeans.10 <- summary(emmeans(lm10,  ~plant), type= "response")

```


Relationship between respiration rate and DOC/SOC
```{r, echo = FALSE}

lm.vif <- lm(sqrt(soil.ugC.hr) ~ (plant + treatment + amendment + doc_ugC + soc_mgC), data = cumu_resp_long)
car::vif(lm.vif)

lm.C1 <- lmer(sqrt(soil.ugC.hr) ~  (plant + treatment + amendment + time_fct)^4 + (1|ring) + 
                (1|ID) + (1|ID:amendment), data = cumu_resp_long)

plot(predict(lm.C1), residuals(lm.C1)) 
qqnorm(residuals(lm.C1)); qqline(residuals(lm.C1))
hist(residuals(lm.C1))

summary(lm.C1)
anova(lm.C1)

cumu_resp_long %>% ggplot(aes(x= plant, y= soil.ugC.hr, color = treatment)) +
  geom_boxplot() + facet_grid(amendment ~ time_fct) + scale_y_continuous(trans = "sqrt")

lm.C2 <- lmer(sqrt(soil.ugC.hr) ~ (soc_mgC + treatment + amendment + time_fct)^4 + 
              (1|ring) + (1|ID) + (1|ID:amendment), data = cumu_resp_long)
anova(lm.C2)

cor.test(cumu_resp_long$soil.ugC.hr, cumu_resp_long$soc_mgC, method = "spearman")

cumu_resp_long %>%  
  ggplot(aes(x= soc_mgC, y= soil.ugC.hr, color = treatment)) +
  geom_point() + geom_smooth(aes(group= interaction(treatment, amendment)), method = "lm")+
  facet_grid(amendment~time_fct) + scale_y_continuous(trans = "sqrt") +
  stat_cor(method = "spearman")


lm.C3 <- lmer(sqrt(soil.ugC.hr) ~ (doc_ugC + treatment + amendment + time_fct)^4 + 
                (1|ring) + (1|ID) + (1|ID:amendment), data = cumu_resp_long)
anova(lm.C3)
summary(lm.C3)

cumu_resp_long %>%  
  ggplot(aes(x= doc_ugC, y= soil.ugC.hr, color = treatment)) +
  geom_point() + geom_smooth(aes(group= interaction(treatment, amendment)), method = "lm")+
  facet_grid(amendment~time_fct) + scale_y_continuous(trans = "sqrt") +
  stat_cor(method = "spearman")
```


Cumulative resp at 4 hours related to DOC/SOC
```{r, echo = FALSE}

resp.4 <- cumu_resp_long %>%  filter(time_fct == "4")

lm.C4 <- lmer(sqrt(cumu.soil.ugC) ~ (plant + treatment + amendment)^3 + (1|ring) + (1|ID), data = resp.4)

plot(predict(lm.C4), residuals(lm.C4)) 
qqnorm(residuals(lm.C4)); qqline(residuals(lm.C4))
hist(residuals(lm.C4))

anova(lm.C4)

cumu.C.4 %>% filter(time_fct == "4") %>% 
  ggplot(aes(x= soc_mgC, y= cumu.soil.ugC, color = treatment)) +
  geom_point() + geom_smooth(aes(group= interaction(treatment, amendment)), method = "lm")+
  facet_grid(~amendment) + scale_y_continuous(trans = "sqrt")


lm.C5 <- lmer(sqrt(cumu.soil.ugC) ~ (soc_mgC + treatment + amendment)^3 + (1|ring) + (1|ID), data = resp.4)
anova(lm.C5)

resp.4 %>% 
  ggplot(aes(x= soc_mgC, y= cumu.soil.ugC, color = treatment)) +
  geom_point() + geom_smooth(aes(group= interaction(treatment, amendment)), method = lm)+
  facet_grid(~amendment)+
  scale_y_continuous(trans = "sqrt") +
  stat_cor(method = "spearman")

lm.C6 <- lmer(sqrt(cumu.soil.ugC) ~ (doc_ugC + treatment + amendment)^3 + (1|ring) + (1|ID), data = resp.4)
anova(lm.C6)

paircomp.C6 <- summary(emmeans(lm.C6, pairwise ~ treatment|amendment)$contrasts)

resp_cumu %>% filter(time_fct == "4") %>% 
  ggplot(aes(x= whc, y= cumu.soil.ugC, color = treatment)) +
  geom_point() + geom_smooth(aes(group= interaction(treatment)), method = lm)+
  scale_y_continuous(trans = "sqrt") +
  stat_cor(method = "spearman")

```

Relationship between cumulative respiration at 168 hours and DOC/SOC

```{r, echo = FALSE}
resp.168 <- cumu_resp_long %>%  filter(time_fct == "168")

lm.C7 <- lmer(sqrt(cumu.soil.ugC) ~ (plant + treatment + amendment)^3 + (1|ring) + (1|ID), data = resp.168)

plot(predict(lm.C7), residuals(lm.C7)) 
qqnorm(residuals(lm.C7)); qqline(residuals(lm.C7))
hist(residuals(lm.C7))

anova(lm.C7)


lm.C8 <- lmer(sqrt(cumu.soil.ugC) ~ (soc_mgC + treatment + amendment)^3 + (1|ring) + (1|ID), data = resp.168)
anova(lm.C8)

resp.168 %>% 
  ggplot(aes(x= soc_mgC, y= cumu.soil.ugC, color = treatment)) +
  geom_point() + geom_smooth(aes(group= interaction(treatment, amendment)), method = lm)+
  facet_grid(~amendment) +
  scale_y_continuous(trans = "sqrt") +
  stat_cor(method = "spearman")

resp.168 %>% 
  ggplot(aes(x= soc_mgC, y= cumu.soil.ugC, color = treatment)) +
  geom_point() + geom_smooth(aes(group= interaction(treatment, amendment)), method = lm)+
  facet_grid(~amendment) +
  scale_y_continuous(trans = "sqrt") +
  stat_cor(method = "spearman")

lm.C9 <- lmer(sqrt(cumu.soil.ugC) ~ (doc_ugC + treatment + amendment)^3 + (1|ring) + (1|ID), data = resp.168)
anova(lm.C9)

resp.168 %>% 
  ggplot(aes(x= doc_ugC, y= cumu.soil.ugC, color = amendment)) +
  geom_point() + geom_smooth(aes(group= interaction(treatment, amendment)), method = lm)+
  facet_grid(~treatment) +
  scale_y_continuous(trans = "sqrt") +
  stat_cor(method = "spearman")

```


Relationship between priming rate and DOC/SOC
Maybe don't include because rates are all right around zero? Or just do 4 hours
```{r, echo = FALSE}
priming <- cumu_resp_long %>% filter(amendment == "glu")

lm.vif2 <- lm(sqrt(abs(primed.ugC.hr)) ~ (plant + treatment + doc_ugC + soc_mgC), 
              data = priming)
car::vif(lm.vif2)

lm.P1 <- lmer(log(abs(primed.ugC.hr)) ~  (plant + treatment + time_fct)^3 + (1|ring) + 
                (1|ID), data = priming)

plot(predict(lm.P1), residuals(lm.P1)) 
qqnorm(residuals(lm.P1)); qqline(residuals(lm.P1))
hist(residuals(lm.P1))

summary(lm.P1)
anova(lm.P1)

lm.P2 <- lmer(log(abs(primed.ugC.hr)) ~ (treatment + soc_mgC + time_fct)^3 + 
              (1|ring) + (1|ID), data = priming)
anova(lm.P2)

cumu_resp_long %>%  
  ggplot(aes(x= soc_mgC, y= primed.ugC.hr, color = treatment)) +
  geom_point() + geom_smooth(aes(group= interaction(treatment)), method = "lm")+
  facet_grid(~time_fct) + 
  stat_cor(method = "spearman")


lm.P3 <- lmer(log(abs(primed.ugC.hr)) ~ (treatment + doc_ugC)^2 + 
                (1|ring) + (1|ID), data = priming)
anova(lm.P3)
```


Cumulative priming at 4 hours related to DOC/SOC
```{r, echo = FALSE}

priming.4 <- cumu_resp_long %>% filter(amendment == "glu") %>% filter(time_fct == "4")

lm.P4 <- lmer(cumu.primed.ugC ~ (treatment +  plant)^2 + (1|ring), data = priming.4)

plot(predict(lm.P4), residuals(lm.P4)) 
qqnorm(residuals(lm.P4)); qqline(residuals(lm.P4))
hist(residuals(lm.P4))

anova(lm.P4)


lm.P5 <- lmer(cumu.primed.ugC ~ (treatment + soc_mgC)^2 + (1|ring), data = priming.4)
anova(lm.P5)

priming.4 %>% 
  ggplot(aes(x= soc_mgC, y= cumu.primed.ugC, color = treatment)) +
  geom_point() + geom_smooth(aes(group= interaction(treatment)), method = lm)+
  scale_y_continuous(trans = "sqrt") +
  stat_cor(method = "spearman")

lm.P6 <- lmer(cumu.primed.ugC ~ (treatment + doc_ugC)^2 + (1|ring), data = priming.4)
anova(lm.P6)

priming.4 %>% 
  ggplot(aes(x= doc_ugC, y= cumu.primed.ugC, color = treatment)) +
  geom_point() + geom_smooth(aes(group= interaction(treatment)), method = lm)+
  scale_y_continuous(trans = "sqrt") +
  stat_cor(method = "spearman")
```

Cumulative priming at 168 hours related to DOC/SOC
```{r, echo = FALSE}

priming.168 <- cumu_resp_long %>% filter(amendment == "glu") %>% filter(time_fct == "168") %>% 
  filter(soc_mgC <= 7)

lm.P7 <- lmer(cumu.primed.ugC ~ (treatment +  plant )^2 + (1|ring), data = priming.168)

plot(predict(lm.P7), residuals(lm.P7)) 
qqnorm(residuals(lm.P7)); qqline(residuals(lm.P7))
hist(residuals(lm.P7))

anova(lm.P7)


lm.P8 <- lmer(cumu.primed.ugC ~ (treatment + soc_mgC)^2 + (1|ring), data = priming.168)
anova(lm.P8)

priming.168 %>% 
  ggplot(aes(x= soc_mgC, y= cumu.primed.ugC, color = treatment)) +
  geom_point() + geom_smooth(aes(group= interaction(treatment)), method = lm)+
  stat_cor(method = "spearman")

lm.P9 <- lmer(cumu.primed.ugC ~ (treatment + doc_ugC)^2 + (1|ring), data = priming.168)
anova(lm.P9)

priming.168 %>% 
  ggplot(aes(x= doc_ugC, y= cumu.primed.ugC, color = treatment)) +
  geom_point() + geom_smooth(aes(group= interaction(treatment)), method = lm)+
  scale_y_continuous(trans = "sqrt") +
  stat_cor(method = "spearman")
```


Correlations
```{r, doc}
corr.data.ctrl <- cumu_resp_long %>% filter(time_fct == "168") %>% 
  filter(amendment == "ctrl")


lm1 <- lm(cumu.soil.ugC ~ doc_ugC, data = corr.data.ctrl)
anova(lm1)

stats::cor.test(corr.data.ctrl$cumu.soil.ugC, corr.data.ctrl$doc_ugC, method = "spearman")
# r = 0.64, p = 7.4x10^-6

ggplot(corr.data.ctrl, aes(x= doc_ugC, y = cumu.soil.ugC, fill = treatment)) + 
  geom_point() + geom_smooth(method = "lm") + facet_grid(~plant)+
  stat_cor(method="spearman", label.y = c(2000), 
           size= 3, r.accuracy = 0.01, p.accuracy =0.01)


corr.data.glu <- cumu_resp_long %>% filter(time_fct == "168") %>% 
  filter(amendment == "glu")

lm2 <- lm(cumu.soil.ugC ~ doc_ugC, data = corr.data.glu)
anova(lm2)

stats::cor.test(corr.data.glu$cumu.net.primed.ugC, corr.data.glu$doc_ugC, method = "spearman")
# r = .77, p = 2.3x10^-7

ggplot(corr.data.glu, aes(x= doc_ugC, y = cumu.net.primed.ugC, fill = treatment)) + 
  geom_point() + geom_smooth(method = "lm") + facet_grid(~plant)+
  stat_cor(method="spearman", label.y = c(600, 800), 
           size= 3, r.accuracy = 0.01, p.accuracy =0.01)

```



```{r, echo = FALSE}
#library(dabestr)

est.data <- cumu_resp_long %>% filter(time_fct == "4") %>% filter(plant == "LATR") %>% 
  filter(amendment == "ctrl")
  

unpaired_mean_diff <- dabest(est.data, treatment, mineralization.hr,
                             idx = c("ambient", "elevated"),
                             paired = FALSE) %>% 
                      mean_diff()

plot(unpaired_mean_diff)


est.data.2 <- cumu_resp_long %>% filter(time_fct == "168") %>% filter(plant == "LATR") %>% 
  filter(amendment == "glu")
  

unpaired_mean_diff.2 <- dabest(est.data.2, treatment, cumu.soil.ugC,
                             idx = c("ambient", "elevated"),
                             paired = FALSE) %>% 
                      mean_diff()

plot(unpaired_mean_diff.2)

```

Priming
```{r, echo = FALSE}
#library(dabestr)

est.data.3 <- cumu_resp_long %>% filter(time_fct == "168") %>% filter(plant == "LATR") %>% 
  filter(amendment == "glu")
  

unpaired_mean_diff.3 <- dabest(est.data.3, treatment, cumu.net.primed.ugC,
                             idx = c("ambient", "elevated"),
                             paired = FALSE) %>% 
                      mean_diff()

plot(unpaired_mean_diff.3)


unpaired_mean_diff.4 <- dabest(est.data.3, treatment, cumu.pos.primed.ugC,
                             idx = c("ambient", "elevated"),
                             paired = FALSE) %>% 
                      mean_diff()

plot(unpaired_mean_diff.4)


unpaired_mean_diff.5 <- dabest(est.data.3, treatment, cumu.neg.primed.ugC,
                             idx = c("ambient", "elevated"),
                             paired = FALSE) %>% 
                      mean_diff()

plot(unpaired_mean_diff.5)

```
